Boutiques: a flexible framework to integrate command-line applications in computing platforms

### 2018-01-26 answers.tex
Minor fixes

\usepackage{hyperref}
\usepackage{xspace}
\newenvironment{review}%          environment name
{\textbf{Reviewer comment:}\begin{quote}}% begin code
{\end{quote}}%  
\newenvironment{answer}%          environment name
{\textbf{Answer:}\begin{small}\begin{quote}}% begin code
{\end{quote}\end{small}}%

@@

\begin{answer}
We thank the reviewer for such a relevant comment. We deliberately
chose to not publish tools to a common repository because we believe
that they should be stored in the tool repositories so that they can
be updated and tested by the tool developers as their implementation
evolves. Instead, the NeuroLinks index provides a way to reference
descriptors without having to store them directly. The search
functionality, however, is a great one and we have discussed the following 
implementation in \texttt{bosh} over the NeuroLinks index.
\begin{enumerate}
\item Make Boutiques entries in Neurolinks immutable:
  \begin{enumerate}
  \item modify bosh publish to commit a URL of a particular commit of the descriptor instead of the latest version.
  \item add the version number of the identifier.
  \item write guidelines to accept PRs about Boutiques descriptors in Neurolinks.
  \end{enumerate}
\item Extend \texttt{bosh} by implementing:
  \begin{enumerate}
  \item \texttt{bosh search} that greps in \url{https://raw.githubusercontent.com/brainhack101/neurolinks/master/jsons/tool.json} and returns a table containing the identifiers and (truncated) descriptions of the Boutiques tools. 
  \item \texttt{bosh get} that downloads a descriptor based on its neurolinks identifier.
  \item \texttt{bosh launch <simulate|exec> <neurolinks\_id>}  that calls \texttt{bosh get} to get the descriptor and launch the tool.
  \end{enumerate}
\end{enumerate}
\end{answer}
This will be implemented as part of issue \href{https://github.com/boutiques/boutiques/issues/34}{34}. We have updated the manuscript accordingly. The paragraph on the Publisher now reads as follows:
\begin{quote}
\emph{Publisher} As Boutiques has primarily been adopted in the neuroinformatics
community, the publisher gets a further description (such as author,
website, etc.) of the described application, and adds an index to it
on
NeuroLinks\footnote{\url{https://brainhack101.github.io/neurolinks}},
a repository containing links to neuroinformatics resources and
tools. We intentionally opted for publishing descriptors to an index
such as NeuroLinks rather than to a common Boutiques repository so
that descriptors remain in the tool repositories and can be maintained
by the tool developers directly. We are currently extending
\texttt{bosh} to enable users to search for Boutiques tools in
NeuroLinks using the command-line or Python API. The publishing
functionality could be extended to new repositories for other domains,
such as Bioconductor for
bioinformatics~\cite{gentleman2004bioconductor}.
\end{quote}

>>>>

\usepackage{hyperref}
\usepackage{xspace}
\newenvironment{review}%          environment name
{\textbf{Reviewer comment:}\begin{quote}}% begin code
{\end{quote}}%  
\newenvironment{answer}%          environment name
{\textbf{Answer:}\begin{quote}}% begin code
{\end{quote}}%

@@

\begin{answer}
We thank the reviewer for such a relevant comment. We deliberately
chose to not publish tools to a common repository because we believe
that they should be stored in the tool repositories so that they can
be updated and tested by the tool developers as their implementation
evolves. Instead, the NeuroLinks index provides a way to reference
descriptors without having to store them directly. The search
functionality, however, is a great one and we have discussed the following 
implementation in \texttt{bosh} over the NeuroLinks index:
\begin{enumerate}
\item Make Boutiques entries in NeuroLinks immutable:
  \begin{enumerate}
  \item modify bosh publish to commit a URL of a particular commit of the descriptor instead of the latest version.
  \item add the version number of the identifier.
  \item write guidelines to accept PRs about Boutiques descriptors in Neurolinks.
  \end{enumerate}
\item Extend \texttt{bosh} by implementing:
  \begin{enumerate}
  \item \texttt{bosh search} that greps in \url{https://raw.githubusercontent.com/brainhack101/neurolinks/master/jsons/tool.json} and returns a table containing the identifiers and (truncated) descriptions of the Boutiques tools. 
  \item \texttt{bosh get} that downloads a descriptor based on its neurolinks identifier.
  \item \texttt{bosh launch <simulate|exec> <neurolinks\_id>}  that calls \texttt{bosh get} to get the descriptor and launch the tool.
  \end{enumerate}
\end{enumerate}
\end{answer}
This will be implemented as part of issue \href{https://github.com/boutiques/boutiques/issues/34}{34}. We have updated the manuscript accordingly. The paragraph on the Publisher now reads as follows:
\begin{quote}
\emph{Publisher.} As Boutiques has primarily been adopted in the neuroinformatics
community, the publisher gets a further description (such as author,
website, etc.) of the described application, and adds an index to it
on
NeuroLinks\footnote{\url{https://brainhack101.github.io/neurolinks}},
a repository containing links to neuroinformatics resources and
tools. We intentionally opted for publishing descriptors to an index
such as NeuroLinks rather than to a common Boutiques repository so
that descriptors remain in the tool repositories and can be maintained
by the tool developers directly. We are currently extending
\texttt{bosh} to enable users to search for Boutiques tools in
NeuroLinks using the command-line or Python API. The publishing
functionality could be extended to new repositories for other domains,
such as Bioconductor for
bioinformatics.
\end{quote}
